D3692R1: How to Avoid OOTA Without Really Trying

### 2025-06-14 paper/ootavacuous.tex
ootavacuous: Note that "carries a dependency" is deprecated
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>
ootavacuous: Remove statement of lack of confidence from section 1.2
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

A \emph{syntactic} dependency, by contrast, exists whenever the value
of the load appears in the source code as part of the computation
leading up to the store, whether it affects the store or not.
Although we will not give a precise definition of syntactic dependency
here, doing so presents no fundamental difficulties.
In fact, the C++ standard covers much of the same ground in its definition
of ``carries a dependency'' in 6.9.2.2p7 (\co{[Data races]}).
Of course, all semantic dependencies are also syntactic.
Note, however, that only semantic dependencies contribute to OOTA.

@@

Moiseenko et al.~avoid cycles in po $\cup$
rf~\cite{EvgeniiMoiseenko2025reexecution}, which might permit
more optimizations than forcing prior relaxed loads to be ordered
before subsequent relaxed stores, but which the authors characterize
as ``(almost) a per-execution model''.
It remains to be seen whether this is close enough to a per-execution
model to be accepted by C++ implementers.
\emph{@@@ I am not fully confident of my characterization of this paper.}

>>>>

A \emph{syntactic} dependency, by contrast, exists whenever the value
of the load appears in the source code as part of the computation
leading up to the store, whether it affects the store or not.
Although we will not give a precise definition of syntactic dependency
here, doing so presents no fundamental difficulties.
In fact, the C++ standard covers much of the same ground in its
(now deprecated) definition
of ``carries a dependency'' in 6.9.2.2p7 (\co{[Data races]}).
Of course, all semantic dependencies are also syntactic.
Note, however, that only semantic dependencies contribute to OOTA.

@@

Moiseenko et al.~avoid cycles in po $\cup$
rf~\cite{EvgeniiMoiseenko2025reexecution}, which might permit
more optimizations than forcing prior relaxed loads to be ordered
before subsequent relaxed stores, but which the authors characterize
as ``(almost) a per-execution model''.
It remains to be seen whether this is close enough to a per-execution
model to be accepted by C++ implementers.
